### 2025-06-25 lecturenotes_aima203/ch5_aima203.tex
chapter 5 exercise

\section{Linearization of Nonlinear Laws}
\begin{enumerate}
\item $\displaystyle y =ax + \frac{b}{x}$ \\[1mm]
This can be written as $xy = b + ax^2$. Put $xy=Y$, $b=A_0$ and $x^2 = X$. Then the given nonlinear equation becomes the linear equation $Y = A_0 + A_1X$.
\end{enumerate}

\item
\end{document}

>>>>

\section{Linearization of Nonlinear Laws}
\begin{enumerate}
\item $\displaystyle y =ax + \frac{b}{x}$ \\[1mm]
  This can be written as $xy = b + ax^2$. Put $xy=Y$, $b=A_0$, $ a= A_1$ and $x^2 = X$. Then the given nonlinear equation becomes the linear equation $Y = A_0 + A_1X$.

  \item $\displaystyle y =ae^{bx}$ \\[1mm]
This can be written as $xy = b + ax^2$. Put $lny=Y$, $lna=A_0$, $b=A_1$ and $x = X$. Then the given nonlinear equation becomes the linear equation $Y = A_0 + A_1X$.
\end{enumerate}

\subsection{Exercise}
\begin{enumerate}
\item Fit a linear equation to the data points with the given weights. \\
  $(0,-1), \, (2,5), \, (5,12), \, (7,20)$ and $W=(1,1,10,1)$
\item Fit the a second-degree polynomial to the given data points: \\
  $(0,71), \, (1,89), \, (2,67), (3,43), \, (4,31), \, (5,18), \, (6,9)$

\item Determine the normal equations for the cubic polynomial fitting.
\item What is the difference between interpolation and curve fitting for a given data points?
\item Convert the following nonlinear equations into suitable linear equations for the curve fitting using linear least square fitting.
  \begin{multicols}{3}
    a). $xy^a=b$
    \columnbreak

    b). $y=ab^x$
    \columnbreak

    c). $y=ax^b$
  \end{multicols}

\item Fit a function of the form $y=ax^b$ to the data points:
  $(61,350), \, (26,400), \, (7,500), (2.6,600)$

\end{enumerate}
\end{document}
